Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-08-12 paper.tex
Continuing with #45
But there's a paragraph I don't know what to do with. Please @pacastillo take a look.

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers, who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can be made, resulting in temporary losses due to a lack of supply
or in bad marketing for the customers, for instance.

Despite the fact that errors in one or the other direction do not have the same impact, it is extremely important to develop an accurate predictive method
which could forecast the future sales a new book will achieve, in order to optimise production schedules, improve the publishing company profits and minimise losses \cite{Zhao2001}, being the latter the main objective of this paper.

It is important to notice that the accuracy of the predictive method that we intend to design is affected negatively by several factors related to decisions on purchases, to freight traffic, or with the distribution strategy \cite{Little1998}.
Thus, it is mandatory to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some variables may have correlations between them, although these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.

>>>>

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers, who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can always be made, resulting in temporary losses due to a lack of supply
or in bad marketing for the customers, for instance. However, in
practice predicting lower sales than the actual ones is not such a big
problem because when inventory is close to exhaustion new print runs
are made; however, this new print run presents the same problem as the
initial one of printing only as many as forecasted, although its cost
is not as hight as the initial one and we are not so concerned with
this issue in this paper.

Despite the fact that errors in one or the other direction do not have
the same impact, it is extremely important to develop an accurate
predictive method 
which could forecast the future sales a new book will achieve, in
order to optimise production schedules, improve the publishing company
profits and minimise losses \cite{Zhao2001}, being the latter the main
objective of this paper.  This is the main problem we are going to
tackle in this paper.

% I don't know what to make with this paragraph. Move it to the
% presentation of the problem, move it to the state of the art, or
% eliminate it completely. Whoever wrote it please help - JJ
It is important to notice that the accuracy of the predictive method
that we intend to design is affected negatively by several factors
related to decisions on purchases, to freight traffic, or with the
distribution strategy \cite{Little1998}. 
Thus, it is mandatory to know the product and the variables that
might affect the sales, and how an expert manager takes them into 
account \cite{Armstrong2001,SThomassey2014}. 
Moreover, their impact is difficult to estimate and it is not constant over time, hence the complexity to adequately identify and measure their influence \cite{DeToni2000}.
In addition, some variables may have correlations between them, although these correlations can be detected using data analysis methods, 
such as Self-Organizing Maps (SOM) \cite{kohonen1998} or stepwise regression analysis (SRA) \cite{Chang2009}.
